### 2021-04-14 paper/ase21/eval.tex
[ASE21] temporal dump

We implemented $\tool$ in Scala by extending $\jiset$, a JavaScript IR-based
semantics extraction toolchain, with a worklist-based fixpoint algorithm for
type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
having uncommon writing styles to $\ires$ instructions, our tool reports
type-related specification bugs detected in fully compiled abstract algorithms.
For built-in libraries, we only targeted essential algorithms for
\jscode{Array}, \jscode{Object}, \jscode{Function}, \jscode{Math},
\jscode{Proxy}, and primitive types.  To evaluate $\tool$, we answer the
following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detcted by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} What is the effect of
    condition-based refinement for type analysis?
  \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
    bugs detected by $\tool$ have?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different \inred{XXX} versions existed in the
official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
the recent three years from January 1, 2018 to March 9, 2021.  We performed our
experiments on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7
and 32GB of RAM.

@@

\todo: extract / type analysis / refinement

@@

\todo: precision / refinement

@@

>>>>

We implemented $\tool$ in Scala by extending $\jiset$, a JavaScript IR-based
semantics extraction toolchain, with a worklist-based fixpoint algorithm for
type analysis.  Since $\jiset$ cannot automatically compiles algorithm steps
having uncommon writing styles to $\ires$ instructions, our tool only reports
type-related specification bugs detected in fully compiled abstract algorithms.
For built-in libraries, we only targeted essential algorithms for
\jscode{Array}, \jscode{Object}, \jscode{Function}, \jscode{Math},
\jscode{Proxy}, and primitive types.  To evaluate $\tool$, we answer the
following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detcted by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} What is the effect of
    condition-based refinement for type analysis?
  \item RQ4: \textbf{(Survey of Detected Bugs)} What kind of properties true
    bugs detected by $\tool$ have?
  \item RQ5: \textbf{(Impact)} How much of an impact does $\tool$ potentially
    have by detecting type-related specification bugs?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different \inred{XXX} versions existed in the
official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
the recent three years from January 1, 2018 to March 9, 2021.  We performed our
experiments on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7
and 32GB of RAM.

@@

\todo: extract / type analysis / refinement?

@@

\todo: precision / refinement?

\subsection{Effect of Refinement}

\todo: refinement -> performance / precision

@@

\subsection{Impact}
